Trail Saving on Backtrack

### 2020-02-18 paper.tex
results

\section{Experiments and Results}
We implemented our techniques in two different SAT solvers, MapleSAT
and Cadical, both of which have finished at or near the top of SAT
competitions for the past several years. Each of these solvers was run
as is without any trail saving or chronological backtracking in one
version, with chronological backtracking in another version, and with
the various types of trail saving we described in the remaining
versions.

We then ran each solver on the 400 benchmarks used in the 2018 SAT
Competition and the 400 benchmarks used in the SAT 2019
Competition. The experiments were run on 2.7 GHz Intel cores with each
process given 7 GB of memory and 5000 seconds of CPU time. We chose
not to output or verify the proofs generated by any of the
solvers. The results are reported in Figure 1.

When comparing regular cadical with non-chronological backtracking
against cadical with trail saving, the average time taken to solve
those instances that were solved by both solvers decreased and the
number of propagations per second increased. Although the total number
of solved instances decreased for both versions of trail saving, the
Par-2 score increased for both of them. The trail saving versions also
solved more instances and had better Par-2 scores than cadical with
chronological backtracking (default parameters).

When comparing regular MapleSAT with non-chronological backtracking
against either of the MapleSAT trail saving versions, the total number
of instances solved increased significantly, the average time taken to
solve those instances which were solved by both solvers decreased, and
the number of propagations per second increased. When comparing the
trail saving versions to MapleSAT with chronological backtracking
(default parameters), the trail saving versions perform slightly
better in both total instances solved and PAR-2 scores.

@@

\begin{figure}
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total Solved & SAT & UNSAT & Par-2 (x 10\textasciicircum{}6 s) \\ \hline
      cadical                  & 492          & 289 &  203  & 3.5020                            \\ \hline
      cadical\_chrono          & 498          & 292 &  206  & 3.4400                            \\ \hline
      cadical\_trail           & 493          & 290 &  203  & 3.5228                            \\ \hline
      cadical\_trail\_enhanced & 496          & 292 &  204  & 3.4847                            \\ \hline
    \end{tabular}
    \caption{Table of results for cadical, version pulled from github as of July 30, 2020.}
\end{figure}

>>>>

\section{Experiments and Results}
For the version of cadical published in
\cite{DBLP:conf/sat/MohleB19}chronological backtracking gives solves 6
more problems and has a lower Par-2 score by a decent margin. When
adding trail saving and all enhancements to the default
non-chronological version of cadical, we end up solving 4 more problems
and the Par-2 score goes decreases by a margin not as good as that
produced by the non-chronological backtracking version. The trail saving
versions improve on the standard non-chronological backtracking but do
slightly worse than the chronological backtracking versions.

For the latest version of cadical that we downloaded as of January 1,
2020, chronological backtracking (set to default parameters)
interestingly makes the solver perform worse than standard
non-chronological backtracking does. This shows that not all solvers
will benefit from chronological backtracking; it depends on the solver's
mix of heuristics and may require fine-tuning the parameters associated
with chronological backtracking. However, after implementing trail
saving and enhancements on top of this version of cadical with
non-chronological backtracking, the solver performs roughly the same as
it does with standard non-chronological backtracking, and does not
suffer a slow down as chronological backtracking appears to.

For MapleSat, chronological backtracking makes a significant improvement
on MapleLCMDist both in terms of total number of problems solved and
Par-2 score. Similarly, trail saving implemented on top of MapleLCMDist
with non-chronological backtracking receives a similarly significant
improvement in terms of total instances solved and Par-2 score, and
actually outperforms chronological backtracking on both measures.

@@

\begin{figure}
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total Solved & SAT & UNSAT & Par-2 (x 10\textasciicircum{}6 s) \\ \hline
      cadical                  & 492          & 289 &  203  & 3.5020                            \\ \hline
      cadical\_chrono          & 498          & 292 &  206  & 3.4400                            \\ \hline
      cadical\_trail           & 493          & 290 &  203  & 3.5228                            \\ \hline
      cadical\_trail\_enhanced & 496          & 292 &  204  & 3.4847                            \\ \hline
    \end{tabular}
    \caption{Table of results for cadical, version pulled from github as of July 30, 2019.}
\end{figure}
